Weather Data Integration and Assimilation System\\

### 2020-02-10 Paper.tex
Dont' use title case of figure captions. Capitalize only the proper nouns. Also, WDIAS can be shorten in figure captions.

TODO: Update content as below, overview of rest of the paper
This paper first provides a short review of the operational forecasting process and the role of Delft-FEWS within that process. Section 3 provides an overview of the philosophy and the most important components and features of Delft-FEWS, while Section 4 discusses some example applications of the Delft-FEWS system in research and operations. A discussion of the systems strengths and limitations is provided in Section 5. Section 6 finally provides a summary of the paper, as well as an outlook on the future development of Delft-FEWS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Modules of Weather Data System}
The figure \ref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system.
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{method/misc/weather_data_system_components.jpg}}
\caption{Components of a Weather Data System.}
\label{fi:wdia_components}
\end{figure}
\paragraph{Integration} The system should capable of integrating data from different source such as satellite data, high end and low end weather station etc. And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally. 
\paragraph{Assimilation} Then the system should be able to fulfill weather models varying data requirements. Also those models reproduce large set of redundant data, thus system should store the bulk data while optimizing the disk space.
\paragraph{Dissemination} Then different users should be able to retrieve data as they required. Also the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Microservice Architecture}
Brief mentioned about soa and Actor model and why moved away from them.
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/k8s_architecture_v3.jpg}}
\caption{\acrfull{k8s} Architecture.}
\label{fi:k8s_architecture}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Structure of \acrshort{wdias}}
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}}
\caption{microservice Architecture - Handle on Demand.}
\label{fi:microservice_architecture_on_demand}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}}
\caption{microservice Architecture - Handle Asynchronously.}
\label{fi:microservice_architecture_async}
\end{figure}

\subsection{Hierarchical Database}
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.4\textwidth]{method/microservice/hierarchical_database.jpg}}
\caption{Hierarchical Database.}
\label{fi:hierarchical_database}
\end{figure}

\subsection{Weather Data Preprocessing}
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.4\textwidth]{method/data_preprocess/summary_weather_data_preprocessing.jpg}}
\caption{Generic Functional Approach to Weather data preprocessing.}
\label{fi:summary_weather_data_preprocessing}
\end{figure}

@@

\subsection{Test Plan and Workload}
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{results/work_load/performance_study_v4.jpg}}
\caption{Performance Study.}
\label{fi:performance_Study}
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{results/obs/all_auto/obs_all_auto_15m_res_latencies_against_hits.png}}
\caption{Performance Test 15min data enabled Auto Scaling - Response Latencies against Server Hits over the elapsed time.}
\label{fi:test_obs_auto_all_15_min_latency_vs_hits}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}}
\caption{Performance Test 15min data enabled Auto Scaling - Transnational Throughput vs Number of Active Threads.}
\label{fi:test_obs_auto_all_15_min_throughput_vs_threads}
\end{figure}

>>>>

TODO: Update content as below, overview of rest of the paper
This paper first provides a short review of the operational forecasting process and the role of Delft-FEWS within that process. Section 3 provides an overview of the philosophy and the most important components and features of Delft-FEWS, while Section 4 discusses some example applications of the Delft-FEWS system in research and operations. A discussion of the systems strengths and limitations is provided in Section 5. Section 6 finally provides a summary of the paper, as well as an outlook on the future development of Delft-FEWS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Modules of Weather Data System}
The figure \ref{fi:wdia_components} shows the basic functions of a Weather data integration and assimilation system.
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{method/misc/weather_data_system_components.jpg}}
\caption{Components of a weather data system.}
\label{fi:wdia_components}
\end{figure}
\paragraph{Integration} The system should capable of integrating data from different source such as satellite data, high end and low end weather station etc. And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally. 
\paragraph{Assimilation} Then the system should be able to fulfill weather models varying data requirements. Also those models reproduce large set of redundant data, thus system should store the bulk data while optimizing the disk space.
\paragraph{Dissemination} Then different users should be able to retrieve data as they required. Also the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Microservice Architecture}
Brief mentioned about soa and Actor model and why moved away from them.
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/k8s_architecture_v3.jpg}}
\caption{\acrfull{k8s} architecture.}
\label{fi:k8s_architecture}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Structure of \acrshort{wdias}}
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}}
\caption{microservice architecture - handle on demand.}
\label{fi:microservice_architecture_on_demand}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}}
\caption{microservice architecture - handle asynchronously.}
\label{fi:microservice_architecture_async}
\end{figure}

\subsection{Hierarchical Database}
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.4\textwidth]{method/microservice/hierarchical_database.jpg}}
\caption{Hierarchical database.}
\label{fi:hierarchical_database}
\end{figure}

\subsection{Weather Data Preprocessing}
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.4\textwidth]{method/data_preprocess/summary_weather_data_preprocessing.jpg}}
\caption{Generic functional approach to weather data preprocessing.}
\label{fi:summary_weather_data_preprocessing}
\end{figure}

@@

\subsection{Test Plan and Workload}
\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{results/work_load/performance_study_v4.jpg}}
\caption{Performance study.}
\label{fi:performance_Study}
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{results/obs/all_auto/obs_all_auto_15m_res_latencies_against_hits.png}}
\caption{Performance test 15min data enabled auto scaling - response latencies against server hits over the elapsed time.}
\label{fi:test_obs_auto_all_15_min_latency_vs_hits}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}}
\caption{Performance test 15min data enabled auto scaling - transnational throughput vs number of active threads.}
\label{fi:test_obs_auto_all_15_min_throughput_vs_threads}
\end{figure}

### 2020-02-10 results/sec_3-observations.tex
Dont' use title case of figure captions. Capitalize only the proper nouns. Also, WDIAS can be shorten in figure captions.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_response_times_vs_threads.png}
    \caption{Performance All Test 60 minutes - Response Time vs Threads}
    \label{fi:test_obs_all_60m_response_vs_threads}
\end{figure}
\ref{fi:test_obs_all_60m_response_vs_threads} show the response time against the number of active threads. As the graph show, the response time kept same while increasing the number of active threads against each test case. This shows the scalability of the \acrshort{wdias}, since the system able to process more requests without a significant change in the latency.
When number of active threads increased more than 122, the \ref{fi:test_obs_all_60m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_res_latencies_against_hits.png}
    \caption{Performance All Test 60 minutes - Latency against server hits}
    \label{fi:test_obs_all_60m_latency}
\end{figure}
\ref{fi:test_obs_all_60m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
The conclusion of giving static latency while increasing the number of requests in \ref{fi:test_obs_all_60m_response_vs_threads} can further prove with this graph, since \ref{fi:test_obs_all_60m_latency} graph gives in details overview over the test plan time span.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_response_times_vs_threads.png}
    \caption{Performance All Test 30 minutes - Response Time vs Threads}
    \label{fi:test_obs_all_30m_response_vs_threads}
\end{figure}
\ref{fi:test_obs_all_30m_response_vs_threads} show the response time against the number of active threads for 30min data. As the graph show, the response time kept same while increasing the number of active threads against each test case. This shows the scalability of the \acrshort{wdias}, since the system able to process more requests without a significant change in the latency.
When number of active threads increased more than 110, the \ref{fi:test_obs_all_30m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data. This graph is similar to the \ref{fi:test_obs_all_60m_response_vs_threads}, but the active thread count goes down as a result of increasing the request size.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_res_latencies_against_hits.png}
    \caption{Performance All Test 30 minutes - Latency against server hits}
    \label{fi:test_obs_all_30m_latency}
\end{figure}
\ref{fi:test_obs_all_30m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
This graph also conclude that, over the time latency does not change very much. But during the peak load, it shows some variation in insert and retrieve of Grid timeseries.
When compared to \ref{fi:test_obs_all_60m_latency}, the latency for insert and retrieve Grid timeseries increase by some amount.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_vs_threads.png}
    \caption{Performance Test - Response Time vs Active Threads}
    \label{fi:test_obs_all_15m_response_vs_threads}
\end{figure}
\ref{fi:test_obs_all_15m_response_vs_threads} show the response time against the number of active threads for 15min data. As the graph show, the response time kept same while increasing the number of active threads against each test case. When number of active threads increased more than 140, the \ref{fi:test_obs_all_15m_response_vs_threads} show uncertainty in the inserting and retrieving all data types. The latency of insert and retrieve Grid timeseries data goes up compared to \ref{fi:test_obs_all_30m_response_vs_threads}.
With higher request size, it become to notice the latency also increase by a small factor when the number of active thread increased. This can clearly notice on with insert and retrieval of Grid timeseries data.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_res_latencies_against_hits.png}
    \caption{Performance Test - Latency against server hits}
    \label{fi:test_obs_all_15m_latency}
\end{figure}
\ref{fi:test_obs_all_15m_latency} graph provides a overview of the variation of latency over elapsed time of the test plan against number of server hits per second for 15min data.
This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan. But at the peak time, it tend to vary from the mean value a lot.
One noticeable fact is, throw out the test time period, it shows spikes in latency when compared to \ref{fi:test_obs_all_60m_latency} and \ref{fi:test_obs_all_30m_latency}.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_transaction_throughtput_vs_threads.png}
    \caption{Performance Test - Transaction Throughput vs Threads}
    \label{fi:test_obs_all_15m_throughtput}
\end{figure}
\ref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against number of active threads.
The formula for total server transaction throughput is \(<active threads> * 1 second / <1  thread response time>\) \cite{JMeterPluginsTransactionPlugin}. Basically, it shows the statistical maximum possible number of transactions based on number of users accessing the application.
With combining the \ref{fi:test_obs_all_15m_latency}, this graph show that the throughput of the system get increased without much change in the latency, thus it proves the scalability of the \acrshort{wdias}.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_percentiles.png}
    \caption{Performance Test - Response times Percentiles}
    \label{fi:test_obs_all_15m_latency_percentile}
\end{figure}
\ref{fi:test_obs_all_15m_latency_percentile} visually shows the summary of \ref{tab:obs_all_15_min_summary} latency up to 90\% percentile. With a higher request size data, the \acrshort{wdias} able to process the requests without significant change in latency up to 90\% percentile.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
    \caption{Performance Import Test 15 minutes data while enabled \acrshort{k8s} Auto Scaling - Latency against server hits}
    \label{fi:test_obs_all_auto_15m_latency}
\end{figure}
\ref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over elapsed time of the test plan against number of server hits per second for 15min data while auto scaling enabled for \acrshort{k8s}.
This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan.
When compared to \ref{fi:test_obs_all_15m_latency}, throw out the test time period, the latency spikes become less.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
    \caption{Performance Import Test 15 minutes data while enabled \acrshort{k8s} Auto Scaling - Transaction Throughput vs Threads}
    \label{fi:test_obs_all_auto_15m_throughtput}
\end{figure}
\ref{fi:test_obs_all_auto_15m_throughtput} shows the total server's transaction throughput against number of active threads.
When compared to \ref{fi:test_obs_all_15m_throughtput}, estimated throughput with higher number of active threads become stable at the graph. Which means enabling auto scaling improve the throughput with higher number of active users as well.

Following charts show the resource usage while running the all test plan while enabling the auto scaling.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_res.png}
    \caption{Performance All Test 15min data - Auto Scaling Resource Usage of Import and Export Modules }
    \label{fi:obs_all_auto_15m_import_export_res}
\end{figure}
\ref{fi:obs_all_auto_15m_import_export_res} show the CPU usage and Memory usage for import timeseries modules and export timeseries modules. The CPU usage shown with milli CPUs \cite{LinuxFoundationManagingKubernetes} (1 CPU = 1000m CPUs) and the Memory usage shown with Megabytes (Mi) \cite{LinuxFoundationManagingKubernetes}. Noticeable, the import-ascii-grid-upload microservice used around 10 CPUs at the peak time while using 3.6 Gb of Memory. Another important fact is, after the test cases finished, the \acrshort{wdias} cool down the system via \acrshort{k8s} auto scaling and release the resources. This clearly shows the elasticity of the \acrshort{wdias} according to the workload.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_grid_pod.png}
    \caption{Performance All Test 15min Interval - Auto Scaling Import ASCII Grid Number of Pods Over Time }
    \label{fi:obs_all_auto_15m_import_grid_pod}
\end{figure}
\ref{fi:obs_all_auto_15m_import_grid_pod} shows the number of import-ascii-grid-upload pods scheduled over time. The auto scaling enabled with the configurations of 1 to 10 pods with the recommended CPU usage with 80\%. And the pods scheduled with 1 CPU requested, and limit with 2 CPUs per pod.
As the graph shows, 3 pods scheduled at the initial as per the configuration of the helm chart. While increasing the workload, new pods get spawn while keeping the constraint of 80\% of recommended CPU utilization. After \acrshort{k8s} spawn 10 maximum pods, it stop spawning new pods. But the pods were able to perform with vertical scaling, since those are not hit the CPU limit of 2.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_adapter_dbs_res.png}
    \caption{Performance All Test 15min Interval - Auto Scaling Resource Usage of Database Adapters }
    \label{fi:obs_all_auto_15m_adapter_dbs_res}
\end{figure}
\ref{fi:obs_all_auto_15m_adapter_dbs_res} shows the resource utilization of database adapters in the \acrshort{wdias}.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/query/obs_query_5m_latency_over_time.png}
    \caption{Performance Query Test over 5 minutes - Response Latency over Time}
    \label{fi:test_obs_query_5m_response_latency}
\end{figure}
\ref{fi:test_obs_query_5m_response_latency} shows the response latency over time for the query test plan. When the number of request get higher, the latency also get increased. That means adapter-query is not very much scalable with the current configurations.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/query/obs_query_5m_response_times_vs_threads.png}
    \caption{Performance Query Test over 5 minutes - Response Latency Times vs Threads}
    \label{fi:test_obs_query_5m_response_times_vs_threads}
\end{figure}
\ref{fi:test_obs_query_5m_response_times_vs_threads} shows the response latency against number of active threads for the query test plan. When the number of server hits get higher, the latency also get increased. That means adapter-query is not very much scalable with the current configurations.

>>>>

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_response_times_vs_threads.png}
    \caption{Load testing with hourly data - Response Time vs Threads}
    \label{fi:test_obs_all_60m_response_vs_threads}
\end{figure}
\ref{fi:test_obs_all_60m_response_vs_threads} show the response time against the number of active threads. As the graph show, the response time kept same while increasing the number of active threads against each test case. This shows the scalability of the \acrshort{wdias}, since the system able to process more requests without a significant change in the latency.
When number of active threads increased more than 122, the \ref{fi:test_obs_all_60m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_res_latencies_against_hits.png}
    \caption{Load testing with hourly data - Latency against server hits}
    \label{fi:test_obs_all_60m_latency}
\end{figure}
\ref{fi:test_obs_all_60m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
The conclusion of giving static latency while increasing the number of requests in \ref{fi:test_obs_all_60m_response_vs_threads} can further prove with this graph, since \ref{fi:test_obs_all_60m_latency} graph gives in details overview over the test plan time span.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_response_times_vs_threads.png}
    \caption{Load testing with 30 minutes data - Response Time vs Threads}
    \label{fi:test_obs_all_30m_response_vs_threads}
\end{figure}
\ref{fi:test_obs_all_30m_response_vs_threads} show the response time against the number of active threads for 30min data. As the graph show, the response time kept same while increasing the number of active threads against each test case. This shows the scalability of the \acrshort{wdias}, since the system able to process more requests without a significant change in the latency.
When number of active threads increased more than 110, the \ref{fi:test_obs_all_30m_response_vs_threads} show uncertainty in the inserting and retrieving Scalar and Vector data. This graph is similar to the \ref{fi:test_obs_all_60m_response_vs_threads}, but the active thread count goes down as a result of increasing the request size.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_res_latencies_against_hits.png}
    \caption{Load testing with 30 minutes data - Latency against server hits}
    \label{fi:test_obs_all_30m_latency}
\end{figure}
\ref{fi:test_obs_all_30m_latency} graph provides a better overview of the variation of latency over elapsed time of the test plan against number of server hits per second.
This graph also conclude that, over the time latency does not change very much. But during the peak load, it shows some variation in insert and retrieve of Grid timeseries.
When compared to \ref{fi:test_obs_all_60m_latency}, the latency for insert and retrieve Grid timeseries increase by some amount.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_vs_threads.png}
    \caption{Load testing with 15 minutes data - Response Time vs Active Threads}
    \label{fi:test_obs_all_15m_response_vs_threads}
\end{figure}
\ref{fi:test_obs_all_15m_response_vs_threads} show the response time against the number of active threads for 15min data. As the graph show, the response time kept same while increasing the number of active threads against each test case. When number of active threads increased more than 140, the \ref{fi:test_obs_all_15m_response_vs_threads} show uncertainty in the inserting and retrieving all data types. The latency of insert and retrieve Grid timeseries data goes up compared to \ref{fi:test_obs_all_30m_response_vs_threads}.
With higher request size, it become to notice the latency also increase by a small factor when the number of active thread increased. This can clearly notice on with insert and retrieval of Grid timeseries data.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_res_latencies_against_hits.png}
    \caption{Load testing with 15 minutes data - Latency against server hits}
    \label{fi:test_obs_all_15m_latency}
\end{figure}
\ref{fi:test_obs_all_15m_latency} graph provides a overview of the variation of latency over elapsed time of the test plan against number of server hits per second for 15min data.
This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan. But at the peak time, it tend to vary from the mean value a lot.
One noticeable fact is, throw out the test time period, it shows spikes in latency when compared to \ref{fi:test_obs_all_60m_latency} and \ref{fi:test_obs_all_30m_latency}.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_transaction_throughtput_vs_threads.png}
    \caption{Load testing with 15 minutes data - Transaction Throughput vs Threads}
    \label{fi:test_obs_all_15m_throughtput}
\end{figure}
\ref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against number of active threads.
The formula for total server transaction throughput is \(<active threads> * 1 second / <1  thread response time>\) \cite{JMeterPluginsTransactionPlugin}. Basically, it shows the statistical maximum possible number of transactions based on number of users accessing the application.
With combining the \ref{fi:test_obs_all_15m_latency}, this graph show that the throughput of the system get increased without much change in the latency, thus it proves the scalability of the \acrshort{wdias}.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_percentiles.png}
    \caption{Load testing with 15 minutes data - Response times Percentiles}
    \label{fi:test_obs_all_15m_latency_percentile}
\end{figure}
\ref{fi:test_obs_all_15m_latency_percentile} visually shows the summary of \ref{tab:obs_all_15_min_summary} latency up to 90\% percentile. With a higher request size data, the \acrshort{wdias} able to process the requests without significant change in latency up to 90\% percentile.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
    \caption{Load testing with 15 minutes data with enabled auto scaling - Latency against server hits}
    \label{fi:test_obs_all_auto_15m_latency}
\end{figure}
\ref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over elapsed time of the test plan against number of server hits per second for 15min data while auto scaling enabled for \acrshort{k8s}.
This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan.
When compared to \ref{fi:test_obs_all_15m_latency}, throw out the test time period, the latency spikes become less.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
    \caption{Load testing with 15 minutes data with enabled auto scaling - Transaction Throughput vs Threads}
    \label{fi:test_obs_all_auto_15m_throughtput}
\end{figure}
\ref{fi:test_obs_all_auto_15m_throughtput} shows the total server's transaction throughput against number of active threads.
When compared to \ref{fi:test_obs_all_15m_throughtput}, estimated throughput with higher number of active threads become stable at the graph. Which means enabling auto scaling improve the throughput with higher number of active users as well.

Following charts show the resource usage while running the all test plan while enabling the auto scaling.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_export_res.png}
    \caption{Load testing with auto scaling resource usage of import and export modules.}
    \label{fi:obs_all_auto_15m_import_export_res}
\end{figure}
\ref{fi:obs_all_auto_15m_import_export_res} show the CPU usage and Memory usage for import timeseries modules and export timeseries modules. The CPU usage shown with milli CPUs \cite{LinuxFoundationManagingKubernetes} (1 CPU = 1000m CPUs) and the Memory usage shown with Megabytes (Mi) \cite{LinuxFoundationManagingKubernetes}. Noticeable, the import-ascii-grid-upload microservice used around 10 CPUs at the peak time while using 3.6 Gb of Memory. Another important fact is, after the test cases finished, the \acrshort{wdias} cool down the system via \acrshort{k8s} auto scaling and release the resources. This clearly shows the elasticity of the \acrshort{wdias} according to the workload.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_grid_pod.png}
    \caption{Load testing with auto scaling import ascii grid number of pods over time.}
    \label{fi:obs_all_auto_15m_import_grid_pod}
\end{figure}
\ref{fi:obs_all_auto_15m_import_grid_pod} shows the number of import-ascii-grid-upload pods scheduled over time. The auto scaling enabled with the configurations of 1 to 10 pods with the recommended CPU usage with 80\%. And the pods scheduled with 1 CPU requested, and limit with 2 CPUs per pod.
As the graph shows, 3 pods scheduled at the initial as per the configuration of the helm chart. While increasing the workload, new pods get spawn while keeping the constraint of 80\% of recommended CPU utilization. After \acrshort{k8s} spawn 10 maximum pods, it stop spawning new pods. But the pods were able to perform with vertical scaling, since those are not hit the CPU limit of 2.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_adapter_dbs_res.png}
    \caption{Load testing with auto scaling resource usage of database adapters.}
    \label{fi:obs_all_auto_15m_adapter_dbs_res}
\end{figure}
\ref{fi:obs_all_auto_15m_adapter_dbs_res} shows the resource utilization of database adapters in the \acrshort{wdias}.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/query/obs_query_5m_latency_over_time.png}
    \caption{Load testing query test over 5 minutes - Response Latency over Time}
    \label{fi:test_obs_query_5m_response_latency}
\end{figure}
\ref{fi:test_obs_query_5m_response_latency} shows the response latency over time for the query test plan. When the number of request get higher, the latency also get increased. That means adapter-query is not very much scalable with the current configurations.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/query/obs_query_5m_response_times_vs_threads.png}
    \caption{Load testing query test over 5 minutes - Response Latency Times vs Threads}
    \label{fi:test_obs_query_5m_response_times_vs_threads}
\end{figure}
\ref{fi:test_obs_query_5m_response_times_vs_threads} shows the response latency against number of active threads for the query test plan. When the number of server hits get higher, the latency also get increased. That means adapter-query is not very much scalable with the current configurations.
